Extending the WebID Protocol with Access Delegation

### 2012-07-31 paper.tex
add abstract

\begin{abstract}
We propose \ldots
\end{abstract}

>>>>

\begin{abstract}
The WebID protocol enables the global identification of agents in a distributed manner by employing cryptography and Linked Data principles.
It is used currently mostly in scenarios where a client wants to access some protected resources on a server.
In order to decide whether access should be granted, the server itself needs to make requests to other servers and retrieve WebID profiles, which contain relationship definitions between agents.
Currenlty those information needs to be publicly available, which leads to an privacy issue, since agents may want to hide such information from the general audience.
In this paper we propose an extension of the WebID protocol, which allows the delegation of access from a WebID to a third party, e.g. a server application.
We describe further use-cases that led to the development of this extension and we discuss the delegation protocol with two reference implementations.
\end{abstract}
